Spin canonical rings of log stacky curves

### 2016-01-13 curves-write-up/AIF/changes-summary.tex
added in references to zhou's thesis

\begin{enumerate}
	\item We added a remark on Gorensteinness of the log canonical ring following
	the definition of a log spin canonical ring in the background section.
	We noticed in comment 1 that the referee made a comment saying
	``Cohen-Macaulay and
projectively Gorenstein follows as usual (of course, provided there are
no log canonical points).'' We were a bit confused about the parenthetical, but interpreted
it to mean that the canonical ring may not be Gorenstein if it is of the form
\begin{align*}
	\oplus_n H^0(X, P + n L)
\end{align*}
for $L$ some fractional divisor and $P$ a point. Of course, in our paper, all canonical rings are of the form
\begin{align*}
	\oplus_n H^0(X, n L)
\end{align*}
for $L$ a fractional divisor, so this would not pose an issue.
	\item Use Hilbert polynomial in Example $\_\_\_$
	\item Replace ``best lower approximation'' with Hirzebruch--Jung
		fractions
	\item (Not to-do yet) Change notation from $\frac{e_i - 1}{2 e_i}$
		to $\frac{e'_i}{2 e'_i + 1}$ where $e'_i = \frac{e_i - 1}{2}$ and
		we range over all $e'_i$ instead of odd $e_i$.
\end{enumerate}

>>>>

\begin{enumerate}
	\item We added a remark on Gorensteinness of the log canonical ring following
	the definition of a log spin canonical ring in the background section.
	We noticed in comment 1 that the referee made a comment saying
	``Cohen-Macaulay and
projectively Gorenstein follows as usual (of course, provided there are
no log canonical points).'' We were a bit confused about the parenthetical, but interpreted
it to mean that the canonical ring may not be Gorenstein if it is of the form
\begin{align*}
	\oplus_n H^0(X, P + n L)
\end{align*}
for $L$ some fractional divisor and $P$ a point. Of course, in our paper, all canonical rings are of the form
\begin{align*}
	\oplus_n H^0(X, n L)
\end{align*}
for $L$ a fractional divisor, so this would not pose an issue.
	\item We included Hilbert polynomial in Examples $3.2- 3.5$.
	\item We included a Remark 2.11 on the existence of generators in degree $0 \bmod r_i$
		and $-2 \bmod r_i$ near the end of subsection 2.1.
	\item We replaced ``best lower approximation'' with Hirzebruch--Jung
		fractions. This not only allowed us to delete the unnecessary, nonstandard definition
		of ``best lower approximation,''
		but also allowed us to shorten and
		clarify our proof of the rather
		technical Lemma 4.4 (which was
		Lemma 4.6 in the previous version).
\end{enumerate}

\section{Other suggestions}
The referee also made the following notational suggestions,
and here we include reasons we would prefer not to implement.

\begin{enumerate}
	\item One suggestion was to change the notation from $\frac{e_i - 1}{2 e_i}$
		to $\frac{s_i}{2 s_i + 1}$ where $s_i = \frac{e_i - 1}{2}$.
		First, we would like to keep our notation because we often
	list degrees of generation and relations by signatures
	of the form $(g; e_1, \ldots, e_n; \delta)$ with bounds given in
	the form $\min(5, e_1, \ldots, e_n)$. These
	seem simpler to
	consider than enumeration by signatures $(g; s_1, \ldots, s_n;
	\delta)$ with bounds given in the form $\min(5, 2s_1 + 1, \ldots,
	2s_n + 1)$. Second, because we will be using $e_i$
	so frequently in our analysis, the paper is shortened
	by writing $e_i$ instead of $2s_i+1$.
	Third, we maintained the $e_i$ notation for consistency
	with the notation established in Voight--Zureick-Brown.
	Fourth, since one of our main applications is to modular forms,
	the number theorists reading it may have an easier time translating
	to modular curves whose signature is written with $e_i$ rather than $s_i$.
	\item One suggestion was to use orbifold terminology instead
		of stacky terminology. Since this paper is in many
		ways intimately tied with Voight--Zureick-Brown,
		we would like to keep the use of stacky terminology
		in order to remain compatible with that paper.
	\item One suggestion was to remove the signature invariant
		and use the more general terminology from the
		Ice cream paper. We agree that it is
		somewhat difficult to generalize the
		signature terminology,
		and we also note that this signature is commonly used in referring
		to modular curves. Since one of the important
		applications of this paper is to rings of modular
		forms, the signature will play a useful role for
		those interested in the translation to modular curves.
		Once again, we would also like to keep the signature
		to remain compatible with Voight--Zureick-Brown.
\end{enumerate}

### 2016-01-13 curves-write-up/spin-cring.tex
added in references to zhou's thesis

@@

@@

To complete the example, it suffices to show there are no
additional relations. 
One method would be to use \cite{buckleyRZ:ice-cream-orbifold-and-riemann-roch}
to write down the Hilbert series and then check this agrees with the
Hilbert series of the ring we constructed above.
Here is an alternative method:
First, note that $a_1 x_1 y_{1, 3} + a_2 x_2
y_{1, 3} + f(x_1, x_2)$ is irreducible because there are no
relations among $x_1, x_2$ and $y_{1, 3}$ in lower degrees. Hence,
$\Bk[x_1, x_2, y_{1, 3}] / (a_1 x_1 y_{1, 3} + a_2 x_2 y_{1, 3} +
f(x_1, x_2))$ is integral and is 2-dimensional. Thus, the map
\eqref{align:surjection} defines a surjection from an integral
2-dimensional ring to a 2-dimensional ring. Therefore, it is an 
isomorphism.
\end{example}

@@

First, by \cite{buckleyRZ:ice-cream-orbifold-and-riemann-roch},
\todo{in theorem 3.1, it states n is at least 2, what is going on?}
the Hilbert series of this log spin curve is
\begin{align*}
	P_{(\sx', 0, \halfcan')}(k) &= \frac{1-2k + k^2 -2k^3 + k^4}{(1-k)^2} + \frac{k^3}{(1 - k)(1 - k^3)} + 2 \frac{k^3 + k^5 + k^7}{(1-k)(1-k^7)}.
\end{align*}
For $k = 0, 1, 2, \ldots$ we have
\[
	P_{(\sx', 0, \halfcan')}(k) = 1, 0, 0, 1, 0, 1, 1, 2, 1, 1, 2, 1, 3, 2, 3, \ldots
\]

@@

Then, there exist constants $\alpha, \beta, \gamma \in \Bk$ so that 
$R_{\halfcan'} \cong \Bk[u, x, y_3, y_4]/(xy_3- \alpha uy_4, y_4^2 - \beta x^2 u - \gamma y^2u).$ The proof of this is fairly algorithmic: We may first 
write down the Hilbert series of $(R_{\halfcan'})_n$ over $\Bk$ using \cite{buckleyRZ:ice-cream-orbifold-and-riemann-roch}, then verify that these generators and relations produce the correct number of independent functions via an analysis of zero and pole order. The details are omitted as it is analogous to Example ~\ref{eg:base-0-377}.
\end{example}

@@

In order to show this is an isomorphism, one can write down the Hilbert series using \cite{buckleyRZ:ice-cream-orbifold-and-riemann-roch} and then use pole order considerations at $P_1$ to check the above relation exists. One can then check that the generators and relation determine a ring with the desired Hilbert series. The verification is analogous to Example ~\ref{eg:base-0-377} and is omitted.
\end{example}

@@

\section{Acknowledgments}
We are grateful to David Zureick-Brown for introducing us to the
study of stacky canonical rings, for providing invaluable guidance,
and for his mentorship. We also thank Ken Ono and the Emory
University Number Theory REU for arranging our project and
providing a great environment for mathematical learning and
collaboration. We thank Brian Conrad, John Voight, and Shou-Wu
Zhang for helpful comments on this paper and thank Jorge Neves
for pointing out the bounds given by Miles Reid's work on the
maximal degrees of minimal generators and relations of spin
canonical rings in high genera. The first author would also like to
mention Joseph Harris and Evan O'Dorney for several enlightening
conversations related to Petri's Theorem. Finally, we gratefully
acknowledge the support of the National Science Foundation (grant
number DMS-1250467). We deeply appreciate all of the support that
has made our work possible.

>>>>

\begin{rem}
	Except in degenerate cases,
	such as when the signature is $(0;3,3,3;0)$
	as covered in the first line of Table ~\ref{table:g-0-exceptional},
	we have the following important restriction on the generators
	of $R_L$. For each $e_i$ in the signature of $\sx$, there
	will be at least one generator
	with degree $0 \bmod e_i$ and at least one generator
	with degree $-2 \bmod e_i$.
	Although this is an important restriction on the genertors,
	we will not use this in the remainder of the paper.
\end{rem}

@@

\begin{rem}
	\label{remark:hilbert-series}
	In the following examples, in order to find the Hilbert series of
	a stacky curve, we will cite
	\cite[Theorem 4.2.1]{zhou:orbifold-riemann-roch-and-hilbert-series}.
	Note that
	\cite[Theorem 3.1]{buckleyRZ:ice-cream-orbifold-and-riemann-roch},
	restates \cite[Theorem 4.2.1]{zhou:orbifold-riemann-roch-and-hilbert-series}
	with the restriction that the dimension of the orbifold (which is the same
	as a stacky curve in dimension 1, by \cite[Proposition 6.1.5]{vzb:stacky},)	
	is strictly more than 1.
	This restriction is made because in birational geometry orbifolds
	usually refer to a normal variety ramified only in codimension at least 2,
	while the stacky points we are dealing with appear in codimension 1.
\end{rem}

@@

To complete the example, it suffices to show there are no
additional relations. 
One method would be to use \cite[Theorem 4.2.1]{zhou:orbifold-riemann-roch-and-hilbert-series}
to write down the Hilbert series and then check this agrees with the
Hilbert series of the ring we constructed above.
Here is an alternative method:
First, note that $a_1 x_1 y_{1, 3} + a_2 x_2
y_{1, 3} + f(x_1, x_2)$ is irreducible because there are no
relations among $x_1, x_2$ and $y_{1, 3}$ in lower degrees. Hence,
$\Bk[x_1, x_2, y_{1, 3}] / (a_1 x_1 y_{1, 3} + a_2 x_2 y_{1, 3} +
f(x_1, x_2))$ is integral and is 2-dimensional. Thus, the map
\eqref{align:surjection} defines a surjection from an integral
2-dimensional ring to a 2-dimensional ring. Therefore, it is an 
isomorphism.
\end{example}

@@

First, by \cite[Theorem 4.2.1]{zhou:orbifold-riemann-roch-and-hilbert-series},
the Hilbert series of this log spin curve is
\begin{align*}
	P_{(\sx', 0, \halfcan')}(k) &= \frac{1-2k + k^2 -2k^3 + k^4}{(1-k)^2} + \frac{k^3}{(1 - k)(1 - k^3)} + 2 \frac{k^3 + k^5 + k^7}{(1-k)(1-k^7)}.
\end{align*}
For $k = 0, 1, 2, \ldots$ we have
\[
	P_{(\sx', 0, \halfcan')}(k) = 1, 0, 0, 1, 0, 1, 1, 2, 1, 1, 2, 1, 3, 2, 3, \ldots
\]

@@

Then, there exist constants $\alpha, \beta, \gamma \in \Bk$ so that 
$R_{\halfcan'} \cong \Bk[u, x, y_3, y_4]/(xy_3- \alpha uy_4, y_4^2 - \beta x^2 u - \gamma y^2u).$ The proof of this is fairly algorithmic: We may first 
write down the Hilbert series of $(R_{\halfcan'})_n$ over $\Bk$ using \cite[Theorem 4.2.1]{zhou:orbifold-riemann-roch-and-hilbert-series},
 then verify that these generators and relations produce the correct number of independent functions via an analysis of zero and pole order. The details are omitted as it is analogous to Example ~\ref{eg:base-0-377}.
\end{example}

@@

In order to show this is an isomorphism, one can write down the Hilbert series using \cite[Theorem 4.2.1]{zhou:orbifold-riemann-roch-and-hilbert-series}
 and then use pole order considerations at $P_1$ to check the above relation exists. One can then check that the generators and relation determine a ring with the desired Hilbert series. The verification is analogous to Example ~\ref{eg:base-0-377} and is omitted.
\end{example}

@@

\section{Acknowledgments}
We are grateful to David Zureick-Brown for introducing us to the
study of stacky canonical rings, for providing invaluable guidance,
and for his mentorship. We also thank Ken Ono and the Emory
University Number Theory REU for arranging our project and
providing a great environment for mathematical learning and
collaboration. We thank Brian Conrad, John Voight, and Shou-Wu
Zhang for helpful comments on this paper and thank Jorge Neves
for pointing out the bounds given by Miles Reid's work on the
maximal degrees of minimal generators and relations of spin
canonical rings in high genera.
We thank Miles Reid for clarifying how to
find the Hilbert series of stacky curves.
The first author would also like to
mention Joseph Harris and Evan O'Dorney for several enlightening
conversations related to Petri's Theorem. Finally, we gratefully
acknowledge the support of the National Science Foundation (grant
number DMS-1250467). We deeply appreciate all of the support that
has made our work possible.
